Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-04 qhtv2.tex
coquilles

\paragraph{Duplicate detection problem.}
We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, E_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$. It is understood that the stream $E_n$ is updated at every time increment. An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, \todo[A verifier using polynomially many resources (time and memory) in $1/\epsilon$].

@@

	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
\end{theorem}

\begin{proof}
	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision. Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e. $h(e_i) = h(e_j)$).

@@

When $|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naive strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w |\Gamma|$ bits of memory.}, both in terms of time and memory. Whether it is possible to bring the value of $M$ below $O(w \log_2 w)$ is an open problem.

>>>>

\paragraph{Duplicate detection problem.}
We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$. It is understood that the stream $E_n$ is updated at every time increment. An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, \todo[A verifier using polynomially many resources (time and memory) in $1/\epsilon$].

@@

	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
\end{theorem}

\begin{proof}
	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision. Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e. $h(e_i) = h(e_j)$). The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.

@@

When $|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naive strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w |\Gamma|$ bits of memory.}, both in terms of time and memory.
